
\cvsection{STRENGTHS}

\cvtag{Mathematics}
\cvtag{Computers}
\cvtag{Programming}
\cvtag{Cryptography}
\cvtag{Logic and Analytic mind}
\cvtag{Responsible}
\cvtag{Hard-working}
\cvtag{Creative}
\cvtag{Teamwork}

\cvsection{Programming aptitudes}

\cvskill{Python}{3}
\cvskill{Java}{3}
\cvskill{Bash}{3}
\cvskill{Latex}{2}
\cvskill{SQL}{2}

\cvsection{Other Skills \& Tools}
\cvtag{Docker}
\cvtag{Excel}
\cvtag{Git}
\cvtag{HMTL}
\cvtag{Maven}
\cvtag{MySQL}
\cvtag{Postman}
\cvtag{RegEX}
\cvtag{SoapUi}
\cvtag{Scrum}
\cvtag{XML}
\cvtag{XSLT}


\cvsection{Languages}

\cvskill{Spanish (native)}{5}

\cvskill{English(B2)}{3}
% \divider

\cvsection{Interests}
Programming in general, but my main focus is in Python and Java.

I also love linux. 

I enjoy reading and watching series.

\cvsection{CERTIFICATES {\tiny (credentials on \href{https://www.linkedin.com/in/jesus-navas-orozco/}{LinkedIn})}} 
% \begin{center}
% (credentials on \href{https://www.linkedin.com/in/jesus-navas-orozco/}{LinkedIn})
% \end{center}
% TODO: PUT IMPORTANT COURSES OF UDEMY HERE
{ \faCertificate \color{emphasis} \hspace{2mm} Cambrigde English Level 2 Certificate in ESOL International (First).}

Official Cambridge Certificate of English at level B2 where my competences are specified to be at level C1.
% \vspace{5mm}

\underline{\textbf{KAGGLE}}

{\faCertificate \color{emphasis} \hspace{2mm} Python (Kaggle).}
{\faCertificate \color{emphasis} \hspace{2mm} Pandas (Kaggle).}

\underline{\textbf{UDEMY}}

{\faCertificate \color{emphasis} \hspace{2mm} SOLID Principles}

{\faCertificate \color{emphasis} \hspace{2mm} Bash Scripting.}

{\faCertificate \color{emphasis} \hspace{2mm} Git Bash for Windows.}

{\faCertificate \color{emphasis} \hspace{2mm} Git, Bitbucket and Sourcetree.}

{\faCertificate \color{emphasis} \hspace{2mm} Introduction to Postman.}

{\faCertificate \color{emphasis} \hspace{2mm} Automate de Boring Stuff with Python.}

{\faCertificate \color{emphasis} \hspace{2mm} Regular Expressions.}

 
%\cvsection{Referencias}

% \cvref{name}{email}{mailing address}

%\cvref{Sebastián Peralta}{sebastian.peralta@alpina.com}
%{3142213052}
%
